Active Learning for Level Set Estimation

### 2013-03-21 msthpres.tex
Various fixes

\begin{frame}
\begin{center}
\vspace{0.2in}
\includegraphics[width=2in]{figures/manual.jpg}\\[-0.5em]
{\tiny (Source: www.limnobotics.ch)}
\end{center}
\end{frame}

\begin{frame}
\begin{center}
\vspace{0.2in}
\includegraphics[width=4in]{figures/boat.jpg}\\[-0.5em]
{\tiny (Source: www.limnobotics.ch)}
\end{center}
\end{frame}

\begin{frame}
\begin{center}
\vspace{0.2in}
\includegraphics[width=4in]{figures/lake.png}\\[-0.5em]
{\tiny (Source: www.limnobotics.ch)}
\end{center}
\end{frame}

\begin{frame}
\begin{center}
\vspace{0.2in}
\includegraphics[width=4.7in]{figures/limno_bgape_sc}
\end{center}
\end{frame}

\begin{frame}
\begin{center}
\vspace{0.2in}
\includegraphics[width=4.7in]{figures/limno_bgape}
\end{center}
\end{frame}

\begin{frame}
\begin{center}
\vspace{0.2in}
\includegraphics[width=4.7in]{figures/limno_bgape_ls}
\end{center}
\end{frame}

\begin{frame}
\begin{center}
\vspace{0.2in}
\hspace{-2em}\includegraphics[width=4.45in]{figures/limno_bgape_cl}
\end{center}
\end{frame}

@@

\begin{frame}
\begin{center}
\includegraphics<1->[width=4in]{figures/limno_bgape_ls}\\[0.5em]
\color{white}
\only<1>{\includegraphics[draft,width=2.3in]{figures/ev_bgape_seq}}
\color{black}
\only<2-4>{\includegraphics[width=2.3in]{figures/ev_bgape_seq}}
\color{white}
\only<2>{\includegraphics[draft,width=2.3in]{figures/ev_bgape_eps}}
\color{black}
\only<3>{\includegraphics[width=2.3in]{figures/ev_bgape_eps}}
\only<4>{\includegraphics[width=2.3in]{figures/ev_bgape_seq_str_sc}}
\only<5>{\includegraphics[width=4in]{figures/limno_bgape_class_354}}
\only<6>{\includegraphics[width=4in]{figures/limno_bgape_str_class_400}}
\only<7>{\includegraphics[width=4in]{figures/limno_bgape_var_class_400}}
\end{center}
\end{frame}

>>>>

\begin{frame}
\begin{center}
\vspace{0.2in}
\only<1>{
\includegraphics[width=2in]{figures/manual.jpg}\\[-0.5em]
{\tiny (Source: www.limnobotics.ch)}}
\only<2>{
\includegraphics[width=4in]{figures/boat.jpg}\\[-0.5em]
{\tiny (Source: www.limnobotics.ch)}}
\only<3>{
\includegraphics[width=4in]{figures/lake.png}\\[-0.5em]
{\tiny (Source: www.limnobotics.ch)}}
\end{center}
\end{frame}

\begin{frame}
\begin{center}
\vspace{0.2in}
\includegraphics<1>[width=4.7in]{figures/limno_bgape_sc}
\includegraphics<2>[width=4.7in]{figures/limno_bgape}
\includegraphics<3>[width=4.7in]{figures/limno_bgape_ls}
\only<4>{\hspace{-2em}\includegraphics[width=4.45in]{figures/limno_bgape_cl}}
\end{center}
\end{frame}

@@

\begin{frame}
\begin{center}
\includegraphics<1->[width=4in]{figures/limno_bgape_ls}\\[0.5em]
\color{white}
\only<1>{\includegraphics[draft,width=2.3in]{figures/ev_bgape_seq}}
\color{black}
\only<2-4>{\includegraphics[width=2.3in]{figures/ev_bgape_seq}}
\color{white}
\only<2>{\includegraphics[draft,width=2.3in]{figures/ev_bgape_eps}}
\color{black}
\only<3>{\includegraphics[width=2.3in]{figures/ev_bgape_eps}}
\only<4>{\includegraphics[width=2.3in]{figures/ev_bgape_seq_str_sc}}
\only<5>{\hspace{-16pt}\includegraphics[width=3.77in]{figures/limno_bgape_class_354}}
\only<6>{\hspace{-16pt}\includegraphics[width=3.77in]{figures/limno_bgape_str_class_400}}
\only<7>{\hspace{-16pt}\includegraphics[width=3.77in]{figures/limno_bgape_var_class_400}}
\end{center}
\end{frame}
